Instructions for COLING-2016 Proceedings

### 2016-07-15 paper/coling2016.tex
add coling

\documentclass[conference,compsoc]{IEEEtran}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

\usepackage{bm}%used for bm
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath} %used for maths symbols
\usepackage{amssymb}%used for empty set symbol
\usepackage{url}
\usepackage{xcolor}% or package color

%used for quotes
\usepackage{epigraph}
\setlength\epigraphwidth{\columnwidth}
\setlength\epigraphrule{0pt}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

%主动感知的
\title{Normal States Training for High Accuracy Event Detection}

\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
%TODO
In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well. 
\end{abstract}

%\textsc{NSDetector} imitates this process automatically in the event detection task, and further verify that the key to improve the accuracy of event detection lies in training the normal states well.

\section{Introduction}
%\textit{``To study the abnormal is the best way of understanding the normal."}---William James
%\textit{``The unpredictable or the rare is more newsworthy than the routine."}---Allan Bell

%The event detection task always tries to find out the newsworthy messages from cyberspace. 
With the increasing of cyberspace data, there is a growing need for detecting events accurately. Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

@@

\begin{figure}
    \label{fig:modelDesc}
    \includegraphics[width=1.0\columnwidth]{img/NSDetectorExample.pdf}
    \caption{\textsc{NSDetector}'s process flow, taking \textbf{military} related events in cyberspace as an example. \textsc{NSDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events, and updates the normal states incrementally by the detected events.}
\end{figure}

For example, in ideal conditions an event detection system for anti-terrorism has the knowledge about the normal state such as “the words ISIS and Syria are both high-frequent, while the word Russia is not so frequent as them”. 
With the knowledge of normal state, the system for anti-terrorism can detect the event of “Russia's anti-ISIS op in Syria” as Russia appeared more frequent than the normal state and appeared with ISIS and Syria. 
After detection, the ideal event detection system also updates the normal state by considering the new coming data.

\section{Related Works}
\subsection{Event Detection}

@@

In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
But they are different from ours.
As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.
\subsection{Knowledge Base}

%Twitter Trending Topic Classification
%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.

%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
%2, 3, 6, 7, 10, 11;
\begin{figure*}[ht]
        \centering
        \label{fig:subfig} %% label for entire figure
        \subfigure[\((0.25,0.25,0.25)\)]{
                \label{fig:subfig:a} %% label for first subfigure a
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
        }
        \subfigure[\((0.5,0.5,0.5)\)]{
                \label{fig:subfig:b} %% label for second subfigure b
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
        } 
        \subfigure[\((0.25,0.25,0.75)\)]{
                \label{fig:subfig:c} %% label for third subfigure c
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
        }
        \subfigure[\((0.5,0.5,1.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure d
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
        }
        \subfigure[\((0.25,0.75,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure e
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
        }
        \subfigure[\((0.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure f
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
        }\hspace{1in}
        \subfigure[\((1.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure g
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
        }
        \subfigure[\((2.5,2.5,2.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure h
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
        }
        \subfigure[\((1.5,1.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure i
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
        }
        \subfigure[\((2.5,2.5,3.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure j
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
        }
        \subfigure[\((1.5,2.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure k
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
        }
        \subfigure[\((2.5,3.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure l
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
        }\hspace{1in}
        \caption{Illustration of Dirichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a,b,g,h) the left four subfigures illustrate the probabilistic density when given the symetric priors for Dirichlet distribution; (c,d,i,j) the central subfigures illustrate the probablistic density given ; (e,f,k,l) }
\end{figure*}

\section{Proposed Method}
\begin{table}
\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline

@@

\subsection{Initialization of Normal States}
In this part, we discuss in detail how to initialize the normal states from the given knowledge base. 
\begin{algorithm}
\caption{Normal States Initialization from Knowledge Base}
\label{alg:normalStatesInit}

@@

\cite{faralli2015large} propose the Twixonomy Graph.

%TODO

\begin{figure}
    \centering
    \includegraphics[width=.85\columnwidth]{img/initializationExample.pdf}  
    \caption{Illustration on how to train normal states from wikipedia,( an approximation to the full history information).}
    \label{fig:modelDesc}
\end{figure}

\subsection{Normal States' Maintenance}
KB-Prior-LDA
\begin{figure}[t]
    \centering
    \includegraphics[width=0.75\columnwidth]{model/lda_tikz.pdf}
    \caption{Probabilistic model for training normal states by using history information.}
    %The convolution neural network for extracting character-level representations of words. Dashed arrows indicate a dropout layer applied before character embeddings are input to CNN.}
    \label{fig:cnn}
\end{figure}

@@

\cite{wallach2008structured}\footnote{\url{https://github.com/mimno/Mallet/blob/master/src/cc/mallet/types/Dirichlet.java}}

@@

\begin{figure}
\centering
\includegraphics[height=3cm]{img/wordClusterGraph.eps}
%todo
\caption{Hot words between the heat pattern forming word time window edge weight calculated by the PMI obtained between words, to obtain spectral clustering clustering clustering}
\label{fig: windowsBurstyWordGraph}
\end{figure}

@@

\textbf{detected events related to micro-blog}
\ \
By algorithm \ref{alg:eventKeywordsSearchMethod} find art \(k \) time window \ \(t \) within the \(| \mathcal{C}_{k, t} | \) events phrase later, you can also further find each event and the corresponding event phrase microblogging.
We looked at the first \(i \) events phrase \(\mathcal{C}_{k, t, i} \),
The phrase based on the number of elements distinguish the event, there are three situations: (1) the phrase event more than two hot words, he said while the event is not a phrase between any two words We have a very strong relationship between the co-occurrence, so just pay attention to the co-occurrence relationship stronger side; (2) event phrase has two hot words; (3) the event is only a hot word in the phrase.
Weibo text length is shorter, not all of the microblogging event will include the phrase \(\mathcal{C}_{k, t, i} \) in all the words.
Such as those on "Apple released the new system mac os lion" event, the event phrase "mac", "os", "lion" does not need to appear in all of the micro-Bo, just check the co-occurrence of a strong relationship between the two words appear together whether in an article in the field \(k \) time window \(t \) micro-Bo: If there is, then added to the events related to the collection \(\mathcal{D}_{k, t, i} \) in.
For the case of a third cluster cluster contains only a hot word, we only need to identify areas \(k \) contains the hot word of all micro-blog, and add the event to the relevant set \(\mathcal{D}_{k, t, i} \) in.
Ultimately, we can get the field \(k \) next time window \(t \) in the event the phrase relating to events microblogging \(\{(\mathcal{C}_{k, t, i}, \mathcal{D}_{k, t, i}) \}_{i=1}^{| \mathcal{C}_{k, t} |} \).

\section{Experiments}
\subsection{Effects of Normal States Initialization}
We use 20newsgroups\cite{lang1995newsweeder} dataset\footnote{http://qwone.com/~jason/20Newsgroups} to check the effects of normal states initialization.

What's NPMI? maybe can refer to \cite{Aletras2013EvaluatingTC}\cite{Rder2015ExploringTS}\footnote{https://github.com/AKSW/Palmetto}.
\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|}
\hline
comp.graphics            & Category:Computer graphics      \\ \hline
comp.os.ms-windows.misc  & Category:Microsoft Windows      \\ \hline
comp.sys.ibm.pc.hardware & Category:IBM personal computers \\ \hline
comp.sys.mac.hardware    & Category:Macintosh computers    \\ \hline
comp.windows.x           & Category:X Window System        \\ \hline
rec.autos                & Category:Automobiles            \\ \hline
rec.motorcycles          & Category:Motorcycles            \\ \hline
rec.sport.baseball       & Category:Baseball               \\ \hline
rec.sport.hockey         & Category:Hockey                 \\ \hline
sci.crypt                & Category:Cryptography           \\ \hline
sci.electronics          & Category:Electronics            \\ \hline
sci.med                  & Category:Medicine               \\ \hline
sci.space                & Category:Outer space            \\ \hline
misc.forsale             & Category:Sales                  \\ \hline
talk.politics.misc       & Category:Politics               \\ \hline
talk.politics.guns       & Category:Gun politics          \\ \hline
talk.politics.mideast    & Category:Middle East           \\ \hline
talk.religion.misc       & Category:Religion               \\ \hline
alt.atheism              & Category:Atheism                \\ \hline
soc.religion.christian   & Category:Christians             \\ \hline
\end{tabular}
\end{table}

\begin{figure}
        \centering
        \includegraphics[height=4.0cm]{img/pmi.pdf}
        \caption{The quality of all twitter topics learned by NS-Prior-LDA increases with normal states weight (\(\lambda\)) before \(\lambda=12.8\). The optimized PMI is gained with moderate normal states weight when considering topics \(k\leq K_{\bm{KB}}\) and topics \(k > K_{\bm{KB}}\) together.}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=1.0\columnwidth]{img/NPMI.pdf}
        \caption{NPMI}
\end{figure}

\begin{table}
\centering
\caption{The PMI of twitter topics learned by NS-Prior-LDA, its variant, and other baselines}
    \begin{tabular}{|l|l|c|}
    \hline
    Model & Prior Knowledge & PMI \\ \hline
    LDA & None  & 1.265 \(\pm\) 0.013     \\ \hline
    BBTM\cite{Yan:2015wm} & None    & 1.467 \(\pm\) 0.017     \\ \hline
    NS-Prior-LDA\(^{(-)}\)   &   \begin{tabular}[c]{@{}l@{}}\footnotesize{Words in categories simply}\\ \footnotesize{extracted from Wikipedia}\end{tabular} & 1.439 \(\pm\) 0.010     \\ \hline
    NS-Prior-LDA         & \begin{tabular}[c]{@{}l@{}}\footnotesize{Normal states initialized} \\\footnotesize{from wikipedia}\end{tabular} & 1.523 \(\pm\) 0.017     \\ \hline
    \end{tabular}
\label{tbl:NS-Prior-LDA}
\end{table}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\scalebox{0.88}{
\begin{tabular}{|cc|cc|cc|cc|cc|cc|}
\hline
\multicolumn{2}{|c|}{\textit{Aviation}} & \multicolumn{2}{c|}{\textit{Health}} & \multicolumn{2}{c|}{\textit{Middle East}} & \multicolumn{2}{c|}{\textit{Military}} & \multicolumn{2}{c|}{\textit{Mobile Phones}} & \multicolumn{2}{c|}{\textit{Video Games}} \\
\begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} & \begin{tabular}[c]{@{}c@{}}Normal\\ States\end{tabular} & \begin{tabular}[c]{@{}c@{}}Topical\\ Words\end{tabular} \\ 
\hline
aircraft & air\scriptsize(3253) & health & weight\scriptsize(16344) & al & \textcolor{red}{\textit{\#syria}}\scriptsize(4212) & army & killed\scriptsize(4055)  & android & iphone\scriptsize (13674) & game & games\scriptsize(8812) \\ 
air & plane & patients & loss & israel & \textcolor{red}{\textit{\#bahrain}} & military & news & mobile & apple & player & liked \\ 
airport & flight & medical & diet & iran & people & air & \textcolor{red}{\textit{\#libya}}\scriptsize(3503) & nokia & android & playstation & free \\ 
flight & time & disease & health & arab & israel & command & libya & ios & app & gameplay & xbox \\
airline & airlines & treatment & cancer & israeli & police & force & rebels & phone & ipad & nintendo & 360 \\
airlines & news & hospital & lose & egypt & \textcolor{red}{\textit{\#libya}}\scriptsize(2557) & regiment & people & samsung & samsung & games & playing \\
aviation & boat & patient & fat & egyptian & \#egypt & forces & police & game & mobile & players & played \\
flying & airport & clinical & tips & ibn & news & squadron & war & app & blackberry & xbox &iphone\scriptsize(2820)\\
pilot & force & symptoms & treatment & jerusalem & \#israel & infantry & libyan & iphone & tablet & mode & time\\
squadron & fly & cancer & body & syria & world & battle & attack & htc & apps & arcade & \textcolor{red}{\textit{ps3}}\\
flights & hurricane & cells & healthy & iraq & syria & commander & u.s. & smartphone & free & wii & trailer\\
pilots & navy & blood & study & palestinian & protest & ship & gaddafi & phones & \#android & multiplayer & online\\
raf & flying & therapy & pain & syrian & israeli & corps & army & blackberry & htc & sega & hours\\
airways & aircraft & drug & exercise & iranian & egypt & navy & forces & apps & google & console & ipad\\
fighter & \textcolor{red}{\textit{irene}} & medicine & \#health & ottoman & al & brigade & pakistan & ipad & galaxy & enemies & app\\
boeing & crew & brain & natural & islamic & syrian & battalion & afghanistan & gsm & ios & characters & player\\
runway & sky & care & disease & iraqi & protesters & lieutenant & military & lte & store & playable & wii\\
force & crash & syndrome & acne & abu & arab & aircraft & attacks & symbian & windows & character & ops\\
crashed & jet & infection & hair & jewish & rights & officer & troops & devices & mac & video & download\\
flew & pilot & disorder & surgery & persian & libya & naval & dead & smartphones & phones & graphics & nintendo\\
\hline
\end{tabular}
}
\end{table*}

\begin{table*}[ht]
\centering
\caption{My caption}
\label{my-label}
\subtable[Twitter Dataset Statistics]{
\begin{tabular}{|l|r|}
\hline
Time range & \begin{tabular}[c]{@{}l@{}}2011/06/30\\ -2011/09/15\end{tabular} \\ \hline
Tweet Number & 36,627,434 \\ \hline
\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark1\end{tabular} & 27 \\ \hline
\begin{tabular}[c]{@{}l@{}}Event Number \\ in Benchmark2\end{tabular} & 523 \\ \hline
\end{tabular}
}\quad \quad
\subtable[Event Detection Results]{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark1\end{tabular} & \begin{tabular}[c]{@{}l@{}}Precision@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}Recall@ \\ Benchmark2\end{tabular} & \begin{tabular}[c]{@{}l@{}}DERate(Duplicate \\ Event Rate)\end{tabular} \\ \hline
    UMass System & 0.882 & 0.138 & 0.941 & 0.071 \\ \hline
    LSH & 0.824 & 0.095 & 0.803 & 0.302 \\ \hline
    TimeUserLDA & 0.353 & 0.536 & 0.071 & 0.054 \\ \hline
    Twevent & 0.824 & 0.697 & 0.641 & 0.113 \\ \hline
    EDCoW & 0.412 & 0.756 & 0.119 & 0.290 \\ \hline
    BBTM & 0.647 & 0.809 & 0.170 & 0.045 \\ \hline
    \textsc{NSDetector} & 1.000 & 0.894 & 0.950 & 0.042 \\ \hline
    \end{tabular}
}
\end{table*}

\begin{table*}[ht]
\centering
\caption{Events about \textit{vehicles} detected by systems between 2011-07-20 and 2011-07-30}
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|c|}
\hline
\multicolumn{1}{|c|}{Date} & \multicolumn{1}{c|}{Event key words} & \multicolumn{1}{c|}{Representative event tweet} & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}Number of \\ event tweet\end{tabular}} \\ \hline
7/20/11 & \begin{tabular}[c]{@{}l@{}}American, airlines, \\ order, planes\end{tabular} & \begin{tabular}[c]{@{}l@{}}NDTV: American Airlines orders 460 new planes from \\ Boeing, Airbus http://bit.ly/p1ZgYG\end{tabular} & 31 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Morocco, military, \\ plane, crash\end{tabular} & \begin{tabular}[c]{@{}l@{}}BBC News - Morocco military plane crash kills 78 \\ http://t.co/uwnLv8L\end{tabular} & 36 \\ \hline
7/27/11 & air, Canada & \begin{tabular}[c]{@{}l@{}}Smoke in galley forces Air Canada flight back to airport. \\ Plane landed safely in Sydney, Australia after dumping fuel\end{tabular} & 48 \\ \hline
7/30/11 & \begin{tabular}[c]{@{}l@{}}Caribbean, airlines, \\ crashes, Guyana\end{tabular} & \begin{tabular}[c]{@{}l@{}}Caribbean Airlines Jet Crash-Lands In Guyana All 163 \\ Passengers, Crew Survive http://t.co/qPVD3WJ\end{tabular} & 57 \\ \hline
\end{tabular}
\end{table*}

\begin{table*}[ht]
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-20 and 2011-07-30}
\label{my-label}
\begin{tabular}{|l|L{3cm}|l|l|}
\hline
Date & Event key words & Representative event tweet & \begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular} \\ \hline
7/20/11 & \begin{tabular}[c]{@{}l@{}}Serbia, crimes, \\ fugitive, arrests\end{tabular} & Serbia: Serbia arrests last war crimes fugitive-TV- Reuters & 27 \\ \hline
7/20/11 & Somalia, famine & \begin{tabular}[c]{@{}l@{}}UN declares famine in Somalia. What can we do to save \\ 3.7million lives? http://bit.ly/r1Rq7R\end{tabular} & 89 \\ \hline
7/21/11 & \begin{tabular}[c]{@{}l@{}}U.S., military, \\accept, gay, \\lesbian, openly\end{tabular} & \begin{tabular}[c]{@{}l@{}}RT @cnnbrk: Pentagon is set to certify that the U.S. military \\ is prepared to accept openly gay and lesbian service members \\ \#dadt\end{tabular} & 20 \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman...˙http://dlvr.it/cLbk8\end{tabular} & 557 \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 25 \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 20 \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 \\ \hline
\end{tabular}
\end{table*}

\begin{figure*}
    \label{fig:algorithm}
    \includegraphics[width=1.0\textwidth]{img/screenShot.png}
    \caption{An illustration of the time series of Military related states on Twitter dataset from 2011-06-30 to 2011-09-15.}
\end{figure*}

\subsection{Data set and experiment settings}
\textbf{Data set.} We conduct the empirical analysis on a twitter dataset which is constructed by \cite{petrovic2012using} and widely used by previous event detection researches \cite{petrovic2013can} \cite{Wurzer:2015wq}. 
Due to the developer policy of Twitter\footnote{https://dev.twitter.com/overview/terms/policy}, \cite{petrovic2012using} only redistributes tweets' IDs\footnote{http://demeter.inf.ed.ac.uk/cross/docs/fsd\_corpus.tar.gz}.
We collected the tweets' contents according to the IDs with the help of Twitter API.

%TODO
The benchmark \textit{Edinburgh twitter corpus} contains 27 manually labeled events\cite{petrovic2013can}\footnote{\url{http://demeter.inf.ed.ac.uk/cross/docs/Newswire_Events.tar.gz}} and 90 million tweets. Though we cannot get the whole dataset due to the limit of Twitter API, after neccessary pre-processing, our rebuilt dataset still contains 36,627,434 tweets, which spans identically from 2011/06/30 to 2011/09/15, and also covers 27 labeled events.
More details of the original dataset are described in \cite{petrovic2010edinburgh}.

20-newsgroup\footnote{http://qwone.com/~jason/20Newsgroups/}

\textbf{Benchmark1} The first set of the ground truth about events in the corpus are provided by \cite{petrovic2013can}, which is mentioned above. 
And 27 events ...

\textbf{Benchmark2} here.

\textbf{Normal States Initialization} here.

\textbf{Baseline}

UMass System

LSH

TimeUserLDA

Twevent

EDCoW

BBTM

\textbf{Model Setting}

\subsection{Validity of Normal States}
\textbf{Topic Coherence} \cite{roder2015exploring}
\subsection{Topical Words Learned by NS-Prior-LDA}
\textbf{PMI}
\subsection{Evaluation of Detected Events}
\textbf{Precision} Precision@Benchmark1, Precision@Benchmark2

\textbf{Recall}

\textbf{Accuracy}

\textbf{DERate(Duplicate Event Rate)}
\subsection{Case Study}

\subsection{Application on Reddit}

>>>>

%
% File coling2016.tex
%
% Contact: mutiyama@nict.go.jp
%%
%% Based on the style files for COLING-2014, which were, in turn,
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{coling2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{bm}%used for bm
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}
\usepackage{amssymb}%used for empty set symbol
\usepackage{amsmath} %used for maths symbols

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\title{Instructions for COLING-2016 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
In the news value theory, the \textit{news unexpectedness} expects the journalists to report the events that are different from the routine things, a.k.a., the normal states. 
For human being, normal states are knowledge learned from news streams and the external environment, and can describe what happened and help to identify what is happening.
In this paper, we propose \textsc{NSDetector}, a high accuracy event detection method that trains normal states better by using knowledge base, which can be treated as the accumulation of happened things. 
In \textsc{NSDetector}, 1) a new data structure \textit{normal states} is proposed to restore what happened; 2) \textit{normal states} can be initialized by knowledge base and further updated by upcoming text streams via our proposed probabilistic model NS-Prior-LDA; 3) events can be detected by normal states with high accuracy.
Experiments on the benchmark \textit{Edinburgh twitter corpus (30 million tweets)} validate the effectiveness of our proposed \textsc{NSDetector}.
\end{abstract}

\section{Introduction}
\label{intro}

With the increasing of cyberspace data, there is a growing need for detecting events accurately. Detecting events can mainly benefit the following three folds: (1) understanding what happened in the corpus without checking every single document manually, and generating the timeline to get a bird's eye view of the corpus\cite{ge2015bring}; (2) being aware what is happening currently, which helps to deal with emergencies\cite{hughes2009twitter}\cite{sakaki2010earthquake}; (3) adding detected events and their types as extra structured data information to organize the unstructured text corpus\cite{ritter2012open}.

@@

\section{Related Works}

@@

In contrast, topic model can handle the lexical variation problem with word co-occurrence\cite{blei2003latent}.
%After \cite{blei2006dynamic} and \cite{wang2006topics} introducing time factor into topic model, a number of temporal model has been developed to different tasks.
As many events are highly related to topics, a number of methods based on topic model have been proposed for event detection, including online detection and offline detection.
Lau\cite{lau2012line} introduces an online topic model to track emerging events in microblogs.
It can deal with a massive of tweets, but it doesn't filter out the tweets related to user interests.
Diao\cite{timeUserLDA2012finding}\cite{diao2013unified} show that event detection can benefit from filtering out user interest related tweets. 
And Yan\cite{Yan:2015wm} models the bursty topic by incorporating burstiness of biterms as prior knowledge.
But they are different from ours.
As these models need the whole dataset as the input, they are offline detections, which is not scalability for large dynamic dataset such as microblogs.

\section{Translation of non-English Terms}

\begin{table}
\begin{tabular}{|p{0.1\columnwidth}|p{0.8\columnwidth}|} \hline
\(G^{(0)}\) & Taxonomy's Graph in Knowledge Base\\ \hline
\(G^{(1)}\) & Category-Page Bipartite Graph in Knowledge Base\\ \hline
\(G^{(2)}\) & Page-Content Bipartite Graph in Knowledge Base\\ \hline
\(c\) & topic related category node in \(G^{(0)}\) and \(G^{(1)}\) \\ \hline
\(K_{\bm{KB}}\) & number of pre-defined topics by Knowledge Base \\ \hline
\(f_{c,w}\) & word \(w\)'s normal state (chi-square score) in category \(c\) \\ \hline
\(\lambda\) & normal state weight in  NS-Prior-LDA\\ \hline
\(\tau_{c,w}\) & word \(w\)'s prior knowledge confidence for topic \(c\) in NS-Prior-LDA\\ \hline
\(S_c\) & topic \(c\)'s all normal states related words \\ \hline
\(K\) & number of topics in NS-Prior-LDA such as \(K>K_{\bm{KB}}\)\\ \hline
\(\mathcal{B}_{c, t}\)  & hot words set detected from topic \(k\) at time \(t\)  \\ \hline
\(\mathcal{G}_{c, t}\)  & hot word graph constructed from \(\mathcal{B}_{c, t}\) \\ \hline
\(\mathcal{C}_{c,t,i}\) & event \(i\)-th related words in topic \(c\) at time \(t\) \\ \hline
\(\mathcal{D}_{c,t,i}\) & event \(i\)-th related tweets in topic \(c\) at time \(t\) \\ \hline
\(\rho\) & density threshold for the sub-graph constructed by event words  \\ \hline

@@

\begin{algorithm}
\caption{Normal States Initialization from Knowledge Base}
\label{alg:normalStatesInit}

@@

@@

@@

@@

\section*{Acknowledgements}

\begin{thebibliography}{}

\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
Alfred~V. Aho and Jeffrey~D. Ullman.
\newblock 1972.
\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
\newblock Prentice-{Hall}, Englewood Cliffs, NJ.

\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
{American Psychological Association}.
\newblock 1983.
\newblock {\em Publications Manual}.
\newblock American Psychological Association, Washington, DC.

\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
{Association for Computing Machinery}.
\newblock 1983.
\newblock {\em Computing Reviews}, 24(11):503--512.

\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
\newblock 1981.
\newblock Alternation.
\newblock {\em Journal of the Association for Computing Machinery},
  28(1):114--133.

\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
Dan Gusfield.
\newblock 1997.
\newblock {\em Algorithms on Strings, Trees and Sequences}.
\newblock Cambridge University Press, Cambridge, UK.

\end{thebibliography}
